---
title: "Central District Drift 2005"
author: "Andy Barclay"
date: "June 21, 2018"
output: html_document
---

##Set up workspace
###Get functions and load tidy packages
```{r workspace setup, echo=TRUE}

source("C:\\Users\\awbarclay\\Documents\\R\\GitHubCloneFunctions.R")#GCL functions
source("LOKI2R_UCIRetro.GCL.R")#This is a modified version of LOKI2R that access a lookup table with addtional attributes for contamination data

library("tidyverse")

```

###Create locus control
```{r locus control, echo=TRUE}

#CreateLocusControl.GCL(markersuite = "Sockeye2011_96SNPs", username ="awbarclay", password = password)#Locus control

sillyvec<-c("SUCICD05","SCDD105","SCDD205","SCDD305","SCDD405","SCDD505","SCDD605","SCDD705","SCDD805","SCDD905")

#LOKI2R_UCIRetro.GCL(sillyvec=sillyvec,username="awbarclay",password)#Pull Data from LOKI

#save.image("V:/Analysis/2_Central/Sockeye/Cook Inlet/2012 Baseline/Mixture/UCI_sockeye_retrospective/CentralDistrictDrift2005.Rdata")

load("V:/Analysis/2_Central/Sockeye/Cook Inlet/2012 Baseline/Mixture/UCI_sockeye_retrospective/CentralDistrictDrift2005.Rdata")
```
###Create inital locus object
This is the list of all 96 loci - may have to drop some loci if they have too much missing data
```{r initial locus object}

loci <- LocusControl$locusnames
loci

```

##Data cleanup
###Check initial sample size
SUCICD05 has only 9 samples because it was analyzed previously under a different silly 
```{r initial sample size, echo=TRUE}

silly_N<-function(sillyvec){sapply(sillyvec,function(silly){get(paste0(silly,".gcl"))$n})}

ColSize<-data.frame(row.names = sillyvec)
ColSize$Original_N <- silly_N(sillyvec)
ColSize

```
###Check genotypes by locus
This is the proportion of the samples with genotypes by locus
```{r sample size by locus}

SampSizeByLoc<-as.tibble(SampSizeByLocus.GCL(sillyvec,loci)/ColSize$Original_N) %>% 
  mutate(Collection=sillyvec) %>% 
  select(Collection,everything()) %>% 
  gather(key=Locus,value="Proportion",-Collection)

head(SampSizeByLoc)
```
####Heatmap to check for holes
```{r heatmap of genotype holes, fig.height=24, fig.width=20}
SampSizeByLoc %>% 
  ggplot(aes(Collection,Locus,fill=Proportion))+
  geom_tile()

```
####Find common locus set
```{r loci to drop}

DropLoci<-SampSizeByLoc %>% 
  filter(Proportion=="0") %>%
  select(Locus) %>% 
  unique() %>% 
  pull(Locus) %>% 
  str_replace_all(pattern=fixed("."), replacement="-")  

```

```{r new locus list}

loci37<-loci[-match(DropLoci,loci)]

write_csv(data_frame(Sockeye_retrospective_37SNPs=loci37),path="Output/Sockeye_retrospective_37SNPs.csv")#This is for adding loci to a new markersuite in LOKI. Note had to delete header in CSV file before importing to the markersuite

```
###New LocusControl
I have to make a new locus control for the 37 loci or many collections will get removed for missing loci.
To do this I had to set up a new markersuite in LOKI for the 37 loci. 
```{r new LocusControl}

```

